---
title: "Final Statistical Inference Project"
output:
  pdf_document: default
  html_notebook: default
  html_document: default
---

## Overview
This is the final statistical inference project. I will investigate the exponential distribution in R and compare it with the CLT. 

```{r}
set.seed(123)
#Distribution of 40 
dist <- rexp(40,.2)
hist(dist)
```

The mean of all of these distributions is as follows:
```{r}
mean(dist)
```
The expected mean is 1/.2 = 5. We get a value close to this, but not exact. We expect other trials to be closer and further.

The variance is done below:

```{r}
var(dist)
```
The variance of the distribution is 17.4, whereas the expected variance is (1/.2)^2 = 25. This is a much larger difference than the mean, presumably because of the outlier in the 20s region. 

Now this will be done 1000 times to see if the average mean is close to the actual mean.

```{r}
mns = NULL
for (i in 1:1000) mns = c(mns, mean(rexp(40,.2)))
hist(mns)
var(mns)
```

As shown in the figure, the distribution is approximately normal. More accurately, the mean has a denser population than the rest, and it is roughly equal drop off on both sides. 






